Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2020-09-28 manuscript/ERL_global_C_review.Rmd
(oops, files didn't actually knit on the last commit)

To test for differences across mature forest biomes, the original values were analyzed via a linear mixed effects model ['lmer' function in 'lme4' R package version **x.xx**; **REF**] with biome as fixed effect and plot nested within geographic.area as random effects on the intercept.
When Biome had a significant effect, we looked at a Tukey's pairwise comparison to see which biomes were significantly different from one another. 
This analysis was run for variables with records for $\ge$7 distinct geographic areas in more than one biome, excluding any biomes that failed this criteria (Table 1).

To test for age trends in young (<100yrs) forests, we employed a mixed effects model with biome and log10[stand.age] as fixed effects and plot nested within geographic.area as a random effect on the intercept.
This analysis was run for variables with records for $\ge$3 distinct geographic areas in more than one biome, excluding any biomes that failed this criteria (Table 1). 
When the effect of stand age was significant at p $\le$ 0.05 and when each biome had records for stands of at least 10 different ages, a biome * stand.age interaction was included in the model.
All database manipulation, analyses, and figure production were fully automated in R (**version, citation**).

>>>>

To test for differences across mature forest biomes, the original values were analyzed via a linear mixed effects model ['lmer' function in 'lme4' R package version **x.xx**; **REF**] with biome as fixed effect and plot nested within geographic.area as random effects on the intercept.
When Biome had a significant effect, we looked at a Tukey's pairwise comparison to see which biomes were significantly different from one another. 
This analysis was run for variables with records for at least seven distinct geographic areas in more than one biome, excluding any biomes that failed this criteria (Table 1).

To test for age trends in young (<100yrs) forests, we employed a mixed effects model with biome and log10[stand.age] as fixed effects and plot nested within geographic.area as a random effect on the intercept.
This analysis was run for variables with records for at least three distinct geographic areas in more than one biome, excluding any biomes that failed this criteria (Table 1). 
When the effect of stand age was significant at p $\le$ 0.05 and when each biome had records for stands of at least 10 different ages, a biome * stand.age interaction was included in the model.
All database manipulation, analyses, and figure production were fully automated in R (**version, citation**).
